---
title: "Sleep Survey Analysis"
author: "Megan McMahon"
date: "2/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)

```

Load sleep data from the redcap export. Use the command head() to preview the dataset.
Clean the data so that:
- The record IDs are reformatted to match sleep variable dataset (imported later)
- Sex and gender are inputted consistently

```{r}
d <- read_csv("~/Box/CogNeuroLab/Aging Decision Making R01/data/AgingDecMem-SleepSurveyData_DATA_2019-09-04_0929.csv")
d <- select(d, -matches("redcap"))

d$record_id <- str_pad(d$record_id, pad = "0", side = "left", width = 4)
d$record_id <- ifelse(d$age <= 30, paste0("3", d$record_id), paste0("4", d$record_id))
d$sex <- factor(ifelse(stringr::str_detect(d$sex, "f|F", negate = FALSE), 0, 1), labels = c("Female", "Male"))
d$age <- as.numeric(d$age)

head(d)

```


This is aggregating sadness, happiness, stress, and rumination by their mean for each subject across the study period, and activity types by each day by their sum across the recording period.

To Do: Sums should be adjusted for length of participation in the study - can divide by total number of days of participation. 

1	activities___1	Attending classes, meetings
2	activities___2	Being physically animated, moving around
3	activities___3	Browsing the internet
4	activities___4	Commuting, traveling
5	activities___5	Doing a favor, helping others
6	activities___6	Doing household chores
7	activities___7	Doing nothing (sitting around, daydreaming)
8	activities___8	Drinking, eating
9	activities___9	Exercising, physical activity, sports
10	activities___10	Hygienic activities (grooming, showering)
11	activities___11	Listening to music
12	activities___12	Playing a game
13	activities___13	Reading
14	activities___14	Resting, napping
15	activities___15	Running errands
16	activities___16	Studying
17	activities___17	Shopping
18	activities___18	Spiritual, religious activity
19	activities___19	Talking, socializing in person
20	activities___20	Texting, talking on the phone
21	activities___21	Thinking, reflecting
22	activities___22	Using social media
23	activities___23	Using a computer
24	activities___24	Walking, running
25	activities___25	Watching TV, movies
26	activities___26	Working
27	activities___27	None of the above

```{r}
d <- d %>% 
  fill(record_id, age, sex) %>%
  filter(!is.na(activities___9))

head(d)

d2 <- merge(select(d, record_id, sex, age), aggregate(. ~ record_id, data=select(d, -sex, -age), FUN=sum), by = "record_id", include.all = FALSE) %>%
  distinct()

ndays <- d %>%
  count(record_id)

d2 <- merge(d2, ndays, by = "record_id")

d2$exercise_prop <- d2$activities___9/d2$n

head(d3)

```

```{r}

```

